Ages of Young Stars and Planets in the Kepler Field

### 2024-06-07 paper/ms.tex
update ms

The stellar ages are given in Table~\ref{tab:planets} for the known
planet hosts, and in Table~\ref{tab:stars} for all Kepler stars.
Figure~\ref{fig:hist_tgyro} shows the rotation-based age distributions
of all the stars (left column) and the KOI hosts (middle column).
These ``histograms'' are sampled from the posterior probability
distributions by drawing ten random samples from each posterior, and
then computing the re-weighted histogram of the resulting samples.
The uncertainties assume Poisson statistics.  We truncated the plots
near $4$\,Gyr since this is the cluster age out to which our
rotational ages are calibrated.  The overall slope yields a paucity of
young stars relative to the expectation of a uniform age distribution.

>>>>

The stellar ages are given in Table~\ref{tab:planets} for the known
planet hosts, and in Table~\ref{tab:stars} for all Kepler stars.
Figure~\ref{fig:hist_tgyro} shows the rotation-based age distributions
of all the stars (left column) and the KOI hosts (middle column).
These ``histograms'' are sampled from the posterior probability
distributions by drawing ten random samples from each posterior, and
then computing the normalized histogram of the resulting samples.
We considered an alternative approach for constructing these
plots using hierarchical Bayesian deconvolution, and found similar results.
The uncertainties assume Poisson statistics.  We truncated the plots
near $4$\,Gyr since this is the cluster age out to which our
rotational ages are calibrated.  The overall slope yields a paucity of
young stars relative to the expectation of a uniform age distribution.
